GPU-friendly Stroke Expansion

### 2024-04-24 paper.tex
Abstract
WIP - note, haven't generated the PDF yet

\begin{abstract}
    Vector graphics includes both filled and stroked paths as the main primitives. While there have been many proposed techniques for rendering filled paths on GPU, stroked paths have proved more elusive. This paper presents a technique for performing stroke expansion, namely the generation of an outline representing the stroke of the given input path, an operation which is considered global, but which we nonetheless implement using a fully parallel algorithm. We introduce several novel techniques, including an encoding of stroked primitives suitable for parallel processing and an Euler spiral based method for computing both flattened parallel curves and approximations to arc segments. Our method produces a near-optimal number of line segments for the filled outline of a stroked cubic Bézier and can be fully evaluated on a GPU with minimal preprocessing.
\end{abstract}

>>>>

\begin{abstract}
    Vector graphics includes both filled and stroked paths as the main primitives. While there are many techniques for rendering filled paths on GPU, stroked paths have proved more elusive. This paper presents a technique for performing stroke expansion, namely the generation of the outline representing the stroke of the given input path. Stroke expansion is a global problem, with challenging constraints on continuity and correctness. Nonetheless, we implement it using a fully parallel algorithm suitable for execution in a GPU compute shader, with minimal preprocessing. The output of our method can be either line or circular arc segments, both of which are well suited to GPU rendering, and the number of segments is minimal. We introduce several novel techniques, including an encoding of vector graphics primitives suitable for parallel processing, and an Euler spiral based method for computing approximations to parallel curves and evolutes.
\end{abstract}
